Water Management

### 2020-02-12 Paper/paper.tex
use cref for nice automatic refences

@@

\begin{document}

@@

In this work, we want to examine the variations in use of water from a (hypothetical) water reservoir.
One of the most important uses of surface water is the irrigation of fields for food production. However, as farming and food production are private enterprises and lakes are public goods, interests of all different parties have to be considered.
The water reservoir to be considered has two stakeholders: farmers, who want to use the water for irrigation purposes and citizens, who want to use the lake for recreational activities.
Note that while looking at just two agents is a vast simplification compared to a real allocation problem, one can easily add more stakeholders to the model, as long as there is enough computational power.
The sequence of events for every period is displayed in figure ~\ref{fig:Sequence}.
At the beginning of every year (Step 1) we have to decide how much of the water from the reservoir is used for the irrigation of fields, which benefits the farmers' harvest.\\\\
The farmers utility function follows the form

@@

Figure \ref{fig:value-function} shows the value function calculated for all possible water levels between the allowed boundaries of 0 and 7. 

@@

Every value along the possible water levels leads to an irrigation amount that optimizes the value for all parties in the given situation. Summarizing these values over the range of possible water levels results in a optimal irrigation policy which is shown in figure \ref{fig:optimal-irrigation-policy}.

@@

A exemplary graph of the mean in every period and the difference to its predecessor is shown in figure \ref{fig:steadyState}.

@@

The result is put in a histogram and shown in figure \ref{fig:steadyStateMonteCarlo}.

@@

Comparing this figure with \ref{fig:rainfall-default} shows a similar shape of the distribution. 

@@

As shown in the changed distribution of rainfalls also has an effect on the optimal irrigation policy since it depends on the expected amount of rain.

>>>>

\usepackage[noabbrev]{cleveref}

@@

\begin{document}
	\let\origref\ref % The original \ref command is now accessible by \origref
	\let\ref\cref    % The command \ref uses \cref from the cleveref package now

@@

In this work, we want to examine the variations in use of water from a (hypothetical) water reservoir.
One of the most important uses of surface water is the irrigation of fields for food production. However, as farming and food production are private enterprises and lakes are public goods, interests of all different parties have to be considered.
The water reservoir to be considered has two stakeholders: farmers, who want to use the water for irrigation purposes and citizens, who want to use the lake for recreational activities.
Note that while looking at just two agents is a vast simplification compared to a real allocation problem, one can easily add more stakeholders to the model, as long as there is enough computational power.
The sequence of events for every period is displayed in ~\ref{fig:Sequence}.
At the beginning of every year (Step 1) we have to decide how much of the water from the reservoir is used for the irrigation of fields, which benefits the farmers' harvest.\\\\
The farmers utility function follows the form

@@

Figure \origref{fig:value-function} shows the value function calculated for all possible water levels between the allowed boundaries of 0 and 7. 

@@

Every value along the possible water levels leads to an irrigation amount that optimizes the value for all parties in the given situation. Summarizing these values over the range of possible water levels results in a optimal irrigation policy which is shown in \ref{fig:optimal-irrigation-policy}.

@@

A exemplary graph of the mean in every period and the difference to its predecessor is shown in \ref{fig:steadyState}.

@@

The result is put in a histogram and shown in \ref{fig:steadyStateMonteCarlo}.

@@

Comparing this with \ref{fig:rainfall-default} shows a similar shape of the distribution. 

@@

As shown in \ref{fig:optimalIrrigationPolicy-real-data} the changed distribution of rainfalls also has an effect on the optimal irrigation policy since it depends ocn the expected amount of rain.
